---
title: "p8105_hw6_bp2678"
author: "Brady Pham"
date: 2023-11-30
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)
library(mgcv)
library(modelr)
set.seed(1)
```

#Question 2 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

#Boot strapped the data and cleaned it

```{r}

boot_strap_results = 
  weather_df |> 
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin +prcp, data = .x)),
    results_log = map(models, broom::tidy),
    results_r2 = map(models, broom::glance)
    ) |> 
    unnest(results_log) |> 
     janitor::clean_names() |> 
    select(id:estimate, results_r2) |> 
    pivot_wider(
      names_from = term,
      values_from = estimate
    ) |> 
    mutate(log_b1b2 = log(tmin * prcp)) |> 
 unnest(results_r2) |> 
  janitor::clean_names() |> 
  select(id, r_squared, tmin, prcp, log_b1b2)

```

#Graph for the r2
```{r}
  boot_strap_results |> 
  ggplot(aes(x = r_squared)) + 
  geom_density() +
  labs(title = "Distribution Graph for R2") +
  theme_bw()
```
In the r2 graph it seems to be a normally distributed graph 


#Graph for the log(b1*b2)
```{r}
  boot_strap_results |> 
  ggplot(aes(x = log_b1b2)) + 
  geom_density() +
  labs(title = "Distribution Graph for log(beta1*beta2") +
  theme_bw()
```
In the the log(b1*b2) graph it seems to be left skewd this may be due to some of the data being missing since the negative values were not accounted for. 

```{r}
boot_strap_results |> 
  summarize(
    ci_lower = quantile(r_squared, 0.025), 
    ci_upper = quantile(r_squared, 0.975))
```
The confidence interval for r squared is (.889, .941)

```{r}
boot_strap_results |> 
  summarize(
    ci_lower = quantile(log_b1b2, 0.025, na.rm = TRUE), 
    ci_upper = quantile(log_b1b2, 0.975, na.rm = TRUE))
```
The confidence interval for log(beta1*beta2) is (-8.96, -4.60)



#Question 3

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") |> 
  janitor::clean_names() |> 
  mutate(across(c(babysex, frace, malform, mrace), as_factor))

Checking_missing_values = 
  birthweight_df |>  
  summarise_all(~sum(is.na(.)))

```

There is no missing values within this dataset. 

```{r}
my_model = lm(bwt ~delwt + mheight, data = birthweight_df)

```
The reason why I hcose delivery weight and mother height is because I believe these play big factors regarding the babies weight. The baby will take all the nutrients from whatever the mom eats and will have genetics that are close to hers.


```{r}
birthweight_df |> 
  modelr::add_residuals(my_model) |> 
  modelr::add_predictions(my_model) |> 
  ggplot(aes(x = fitted.values(my_model), y = residuals(my_model))) + geom_point() +
  theme_bw()
```

My residuals plot look fairly symmetrical and fairly distribute with around 2 outliers.


#Setting up the two models from the problem
```{r}
main_only = lm(bwt ~ blength + gaweeks, data = birthweight_df)

interaction = lm(bwt ~ bhead + blength + babysex + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight_df)

```


```{r}
cv_df =
  crossv_mc(birthweight_df, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```


```{r}
cv_df = 
  cv_df %>% 
  mutate(
    main_only = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interaction = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + babysex*bhead + babysex*blength
                                      + bhead*blength + babysex*bhead*blength, data = .x)),
    my_model = map(.x = train, ~lm(bwt ~delwt + mheight, data = .x))) |> 
    mutate(
    rmse_main_only = map2_dbl(.x = main_only, .y = test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(.x = interaction, .y = test, ~rmse(model = .x, data = .y)),
    rmse_my_model = map2_dbl(.x = my_model, .y = test, ~rmse(model = .x, data = .y))
  )

```

#Plotting 


```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) |> 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  theme_bw()
```

According to the three graphs, the best model would be the model with the interaction due to the rmse having the lowest value. Then it would be the model with the main effects only and no interaction. My model would be last because of the high rmse value. The reason for my model to have a high rmse value could be the fact that I only consider variables that invovled the mom and not other external factors. 













